Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles

### 2021-05-04 source/tex/ladybug_adhesion.tex
minor comments of referees implemented partially

\title{Wetting of the adhesive fluid controls underwater adhesion in insects}

@@

\keywords{adhesion; capillary force; underwater;  beetle; gecko}

@@

Many insects can climb smooth surfaces using hairy adhesive pads on their legs. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extent such an air bubble is necessary for underwater adhesion. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the adhesive fluid secretion alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. 
\end{abstract}

@@

The question on how insects and other small arboreal animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}. We now know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion. All insect pads secrete an adhesive fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion using secreted liquids (glue-like substances or the adhesive fluid) requires the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that a terrestrial leaf beetle can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remained unclear whether an air bubble is strictly necessary and its exact contribution to the adhesive force. The oily adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hairs when submerged. In beetles, the tip of each seta secretes approximately one femtoliter of adhesive fluid \cite{RN108}. The fluid's chemical composition was identified to be an oil-like mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol\cite{RN221,RN222}, rendering it immiscible with water.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We characterised adhesion by the pull-off force
during detachment, tested on smooth glass and
fluorinated surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the contact type
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact types were compared for both substrates.

@@

Seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water \emph{ad libitum}.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.) allowing us to further align the leg to the substrate. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate. Each leg of a male ladybug beetle has two pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The sensor was mounted on a stage
consisting of a X-piezo element, used for precise lateral movements, XYZ motors,
for coarse movements and a goniometer, for adjusting substrate alignment
with the optics. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. A coaxial illuminated tube microscope
(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 px; \emph{Basler ace U}, 1280 x 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of epi-illumination.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

@@

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
the pad was brought into contact with the surface 10 times repeatedly 
to equilibrate the pad's secretion system.

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion setup (for explanation see text). The recorded force data and
contact area of a distal pad are shown in the plot, in which, the shaded
regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material.}
\end{figure}

@@

Extraction of pull-off force from force data, image processing, plotting
and statistical analysis were all performed in ``\emph{Buggee}'',
a tool written in Python using open-source libraries for synchronous
analysis of force data and video recordings (\url{https://github.com/PranavSudersan/Buggee}).

For measurements in air, the pull-off force was defined as the minimum
negative force during the final retraction step (Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension effects. This effect needed to be cancelled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing single
leg adhesion force measurements of ladybug beetle (\emph{Coccinella
septempuctata}) on glass and PFOTS substrates in air and underwater
conditions. The two types of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair height = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the adhesive fluid in air and water were assumed to be
24 mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
\end{figure}

@@

FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
leg when underwater (Table \ref{tab:Molecular-distribution-of}).
Molecular weights of the secreted fluid mixtures extracted from the
beetle's leg, without and after immersion in water, show that, except
for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
fingerprint remained unchanged This indicates that the adhesion fluid
was not washed away underwater. Probable compounds in the fluid, corresponding
to the resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
to assert that, even for the case of \emph{Coccinella
septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments.

@@

The net force in the \emph{underwater: bubble} case mainly depends
on the proportion of hairs inside and outside the bubble (equation
(\ref{eq:f_bubble})). For the given bubble volume, only part of the
hairs are inside the bubble for the hydrophilic substrate, while,
all the hairs are inside the bubble for the hydrophobic substrate.
Therefore, the force curve lies between \emph{in air} and \emph{underwater:
no bubble} cases for a hydrophilic substrate, and closely follows
the \emph{in air} case for a hydrophobic substrate.

@@

The bubble's contribution gets repulsive as hair diameter decreases
for both substrates (Figure \ref{fig:Effect-of-hair}). Since the
aspect ratio $L/D_{h}$ is fixed (Table \ref{tab:Model-parameters}),
decreasing the hair diameter also decreases its length. Since the
bubble's volume is kept constant, it will then have a lesser space
available to occupy between the pad and the substrate, This results
in it bulging outwards near the pinned contact line on the top, causing
repulsion.

@@

The findings can also be extended to other animals relying on oily
secretions for adhesion. Some ants, for example, show similar adhesion
on hydrophobic substrates under wet and dry conditions \cite{RN213},
similar to what we see in a ladybug. Recent experiments on
geckos revealed that they can attach well to fluoropolymer substrates
underwater while they show little adhesion to the same substrate in
air\cite{RN199,RN15}. Geckos are thought to rely on van der Waals
forces via dry contact with the substrate \cite{RN202}, although
recent observations of phospholipid footprints left behind walking
geckos \cite{RN205} could change that picture. Since geckos adhere
poorly to PTFE (surface energy $\sim$ 20 mN/m) one can
speculate that the phospholipid material has a higher surface energy,
and consequently makes a higher contact angle with PTFE in air. Let
us assume the phosopholipid substance to be a fluid similar to oil
with $\gamma_{fa}$= 30 mN/m and $\gamma_{fw}$= 42 mN/m such that
its contact angle with PTFE is 80\textdegree . Equation \ref{eq:theta_fw}
then gives us an underwater contact angle of 70\textdegree{} for the
phospholipid fluid. Thus, on a PTFE surface, the capillary bridge
model can predict a higher adhesion underwater than in air due to
its lower contact angle and higher interfacial energy underwater.
Based on similar assumptions, we predict the net adhesion force for
the gecko on different substrates (Figure \ref{fig:Comparison-with-model}).
The adhesion force predictions are in good qualitative agreement with
the whole animal experimental shear force values reported for the
gecko, with the trend of higher adhesion in air than underwater for
glass, similar adhesion in air and underwater for PMMA/OTS-SAM and
lower adhesion in air than underwater for PTFE. We, thus, propose
that the underwater experiments performed on geckos \cite{RN199,RN15}
indicate a capillary contribution to gecko adhesion. We suggest performing
single seta adhesion force tests similar to \citet{RN202}
using a hydrophilic and fluorinated probe in air and underwater conditions
to validate the role of capillary contributions to gecko adhesion.

>>>>

\title{Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles}

@@

\keywords{bio-adhesion; capillary force; bubble; insects; gecko}

@@

Many insects can climb smooth surfaces using hairy adhesive pads on their legs. It was previously shown that a terrestrial beetle can even adhere and walk underwater. The naturally hydrophobic hairs trap an air bubble around the pads, allowing the hairs to make contact to the substrate like in air. However, it remained unclear to what extent such an air bubble is necessary for underwater adhesion. To investigate the role of the bubble, we measured the adhesive forces in individual legs of live but constrained ladybug beetles underwater in the presence and absence of a trapped bubble and compared it with its adhesion in air. Our experiments revealed that on a hydrophobic substrate, even without a bubble, the pads show adhesion comparable to that in air. On a hydrophilic substrate, underwater adhesion is significantly reduced, with or without a trapped bubble. We modelled the adhesion of a hairy pad using capillary forces. Coherent with our experiments, the model demonstrates that the wetting properties of the tarsal adhesive fluid secretion alone can determine the insects' adhesion in both air and underwater conditions and that an air bubble is not a prerequisite for their underwater adhesion. 
\end{abstract}

@@

The question on how insects and other small animals climb smooth and slippery
surfaces has fascinated scientists for the past three centuries \cite{RN198,RN59}. We know that such animals are able to adhere by using specialised organs on their feet called adhesive pads. These adhesive pads can generally be described as either ``smooth'' or ``hairy''. Several insect orders including earwigs, flies, and beetles \cite{Gorb:2001b} but also several spiders \cite{Coddington:1991} and arboreal lizards \cite{Williams:1982} bear hairy pads. Hairy pads show 1) compliance to rough surfaces due to their lower effective modulus, 2) angle dependent adhesion due to asymmetric hair geometry and 3) self-cleaning capability \cite{RN20}, which makes them suitable to adhere to most surfaces reversibly. The hairs themselves (setae) can branch into smaller fibrillar units (spatulae) as seen in spiders and lizards but are typically undivided in most insects. The hairs in many insects can however exhibit different tip geometries, including discoidal, spatula shaped or pointed tips, and distributed throughout the pad depending on sex or species\cite{RN19}. Single seta force measurements revealed that discoidal shaped seta show larger pull-off forces than spatula shaped or pointed setae\cite{RN79}, illustrating the role of hair geometry in adhesion. Insect tarsal hairs secrete an adhesion-mediating fluid (``wet adhesion'') while spiders and geckos rely on their dry hairy pads for attachment (``dry adhesion''). In the ``wet adhesion'' case, fluid secretion can enforce adhesion through surface tension and viscous forces \cite{RN71}, while, ``dry adhesion'' relies mostly on van der Waals forces \cite{RN202}.

While most of the studies on insect adhesion focused on terrestrial species, underwater insect attachment is much more rare and has been relatively unexplored. Some aquatic insects like diving beetles \cite{Chen:2014} or midge larva \cite{Kang:2020} use suction cups to adhere to surfaces. However, underwater adhesion mediated by secreted liquids require the displacement of the water at the interface first and a spreading of the fluid on the substrate. One relatively simple approach is to use an air bubble around the adhesive organs similar to the air bubbles many secondary aquatic insects and spiders carry on their body for breathing underwater \cite{Seymour:2013}. This has been shown in a recent study by \citet{RN87} that that female terrestrial green dock beetles \emph{Gastrophysa viridula} can attach quite well to surfaces underwater by using such an air bubble. Their naturally hydrophobic tarsal hairs trap the bubble around the pads when being submerged, which de-wets the surface effectively on contact. It has been hypothesised that a combination of capillary forces due the air bubble and hair secretions within the de-wetted area results in its adhesion underwater. However, it remains unclear if an air bubble is necessary for adhesion and what, if any, contribution it has to the adhesive force. The oily tarsal adhesive fluid found in insects alone might be sufficient in creating the necessary capillary adhesion even without a bubble, given that the fluid remains on the hairs when submerged. In ladybug beetles, the tip of each seta secretes approximately one femtoliter of adhesive fluid by each step \cite{RN108}. The fluid's chemical composition in green dock beetles was identified to be an oil-containing mixture of mostly long chain hydrocarbons\cite{RN96} with traces
of triglycerides, fatty acids and cholesterol in ladybirds \emph{Hemisphaerota cyanea} and \emph{Epilachna vingtipunctuata}\cite{RN221,RN222}, rendering it immiscible with water.

@@

Normal adhesion force measurements on a restrained leg in a live
beetle were performed. We characterised adhesion by the pull-off force
during detachment, tested on smooth normal and
fluorinated glass surfaces representing hydrophilic and hydrophobic substrates
respectively. When no water was present, we labelled the mode of contact
as ``\emph{in air}''. Underwater, measurements
were done both in the presence and absence of a trapped air bubble (``\emph{underwater:
bubble}'' and ``\emph{underwater: no bubble}'', respectively) to
investigate the air bubble's role in underwater adhesion. Adhesion force
for each of the labelled contact modes were compared for both substrates.

@@

The seven-spotted male adult ladybug beetles (\emph{Coccinella septempuctata})
were purchased from Katz Biotech (Baruth, Germany) and housed in a plastic box filled with leaves,
twigs and stones at room temperature and 60-80\% relative humidity
with daily access to sunlight. They were fed with raisins, honey and
water \emph{ad libitum}.

 %The beetle's leg was constrained similar to the method described by Bullock et al \cite{RN19}.
An individual beetle was first carefully anaesthetised using small amounts of CO\textsubscript{2} sublimating
from a piece of dry ice and then glued with a small dollop of epoxy glue on its elytra to the underside of a heavy steel ball. The ball was held in a bracket which allowed free rotational movement of the ball in each direction, thus helping to align the suspended beetle over the substrate (see Fig.~\ref{fig:Setup}). The bracket with the ball and the beetle could be further positioned by manual micro-manipulators in all three axes before the experiments. One front left leg was carefully fixed to a piece of soft solder wire coming off the steel ball using Blu Tack (Bostik Ltd., U.K.) allowing us to further align the leg to the substrate. The claws on the leg were also fixed to the wire using epoxy glue to prevent any further wiggling and to prevent the claws from touching the substrate. Care was taken to ensure the glue doesn't contaminate the pads. Each leg of a male ladybug beetle has two pads. For the test, we only allowed the distal pad to come into contact with the substrate thus minimising partial or bad contact of the other one. A small piece of non-sticky Teflon tape helped to keep other legs tucked close to the body and avoided any interference during the adhesion test. After the measurements, the beetle was freed by carefully removing the epoxy glue and Blu Tack without harming it and set free.

@@

Adhesion measurements were performed on a custom force measurement
setup developed in-house (Figure \ref{fig:Setup}). A fibre optic
displacement sensor (\emph{Philtec D20, PHILTEC, Inc. USA}) together
with a steel bending beam (spring constant = 68.1 N/m) constitutes
the vertical force sensor. Beam deflection was calibrated using 4
different known weights to get the corresponding force. A plastic
3D printed substrate holder was glued to the end of the bending beam.
The holder was designed to enable switching from one substrate to
another without removing any glue. It also had transparent side walls
which allowed us to fill it with water for the underwater experiments
as well as observe the contact. The force sensor was mounted on a stage
consisting of a X-piezo element, used for precise lateral movements. Additionally, a separate Z-piezo element, fixed upright,
was used for vertical up-down motion, bringing the insect in contact
with the substrate from the top. Coarse movements of the bottom stage were done using the XYZ motors.
A coaxial illuminated tube microscope
(\emph{Navitar}) with 2$\times$ objective and a stereo-microscope
with 1$\times$ objective (\emph{Wild Heerbrugg}) fit with digital video cameras (\emph{FLIR Blackfly S}, 2448 x 2048 px; \emph{Basler ace U}, 1280 x 1024 px)
were used to record the sample contact with the substrate from ventral
and side views respectively. Pad contact area was visualised through
the substrate under reflection mode with the help of co-axial illumination. A goniometer was used to adjust the substrate alignment
with the ventral view optics to achieve total internal reflection.
The data acquisition from the force sensor and cameras, together with
the appropriate piezo motion steps were synchronised using a custom
LABVIEW program. Force data was acquired at a sample rate of 984 Hz,
averaged to 512 points per motion step. Videos were recorded at 20
frames per second.

@@

For underwater experiments, 1 ml Milli-Q water was pipetted into the
substrate holder. In order to achieve an underwater contact without
a trapped air bubble, the water was first degassed in a vacuum chamber
at 10 mbar pressure for 3 hours and used immediately. Before the experiments,
the pad was brought into contact with the dry surface 10 times repeatedly 
to equilibrate the pad's secretion system.

@@

\begin{figure}[H]
\begin{centering}
\includegraphics[scale=0.5]{Figure1-Setup_schematic}
\par\end{centering}
\caption{\label{fig:Setup} Adhesion test setup (for explanation see text). The recorded force data and
contact area of a distal pad are shown in the plot, in which, the shaded
regions from left to right represent the distinct movement sequence: approach, lateral pull, approach, pause and retract, respectively. Negative force values
represent attraction and the minimum force peak during the final retraction
step is the adhesion force used for further analysis. An animated version of a typical force recording is available in the Supplementary Material.}
\end{figure}

@@

Extraction of pull-off force from force data, image processing, plotting
and statistical analysis were all performed in ``\emph{Buggee}'',
a software tool written in Python using open-source libraries for synchronous
analysis of force data and video recordings (\url{https://github.com/PranavSudersan/Buggee}).

For measurements in air, the pull-off force was defined as the minimum
negative force during the final retraction step (Figure \ref{fig:Setup}).
For underwater measurements, an additional correction was necessary.
When the beetle was partially submerged underwater, its contact line at the
water surface shifted, which influenced the force readout due to surface
tension and buoyancy. This effect needed to be cancelled. So, a ``background''
force data was recorded, where the submerged beetle makes no contact
with the substrate. This background data was then subtracted from
a typical force data with substrate contact to correct for the external
surface tension effects. The pull-off force was subsequently calculated
from the minima as before.

@@

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{Figure2-Expt_effect_of_contact}\caption{\label{fig:Effect-of-contact}Box-and-whisker plot showing single
leg adhesion force measurements of ladybug beetle (\emph{Coccinella
septempuctata}) on glass and PFOTS substrates in air and underwater
conditions. The two modes of contact during underwater experiments
are represented separately: \textquotedblleft\emph{bubble}\textquotedblright{}
and \textquotedblleft\emph{no bubble}\textquotedblright . Crosses
represent theoretical predictions of adhesion force, while, circles
represent the contribution of the bubble itself, calculated from the
capillary bridge model. In the model, hair diameter = 4 \textmu m,
pad diameter = 200 \textmu m, hair height = 40 \textmu m,
N\protect\textsubscript{hairs} = 500, V\protect\textsubscript{fluid}
= 4.2 fL and V\protect\textsubscript{bubble} = 1.2 nL. Interfacial
tension of the adhesive fluid in air and water were assumed to be
24 mN/m and 48 mN/m respectively and water surface tension is 72 mN/m.}
\end{figure}

@@

FDMS results confirm the presence of adhesive fluid on an Asian ladybird's
leg when underwater (Table \ref{tab:Molecular-distribution-of}).
Molecular weights of the secreted fluid mixtures extracted from the
beetle's leg, without and after immersion in water, show that, except
for two molecular weights (406.8 g/mol and 331.6 g/mol), the chemical
fingerprint remained unchanged. This indicates that the adhesion fluid
was not washed away underwater. Probable compounds in the fluid, corresponding
to the resultant molecular weights, include mostly aliphatic hydrocarbons
with traces of aldehydes. Our preliminary measurements on \emph{Harmonia axyridis} gives us confidence
to assert that, even for the case of \emph{Coccinella
septempuctata}, the adhesive fluid was not washed away from the hairs during the underwater experiments.

@@

The net force in the \emph{underwater: bubble} case mainly depends
on the proportion of hairs inside and outside the bubble (equation
(\ref{eq:f_bubble})). For the given bubble volume, only part of the
hairs make contact with the surface inside the bubble for the hydrophilic case, while,
all the hairs contact the surface inside the bubble for the hydrophobic case.
Therefore, the force curve lies between \emph{in air} and \emph{underwater:
no bubble} cases for a hydrophilic substrate, and closely follows
the \emph{in air} case for a hydrophobic substrate.

@@

The bubble's contribution gets repulsive as hair diameter decreases
for both substrates (Figure \ref{fig:Effect-of-hair}). Since the
aspect ratio $L/D_{h}$ is fixed (Table \ref{tab:Model-parameters}),
decreasing the hair diameter also decreases its length. Since the
bubble's volume is kept constant, it will then have a lesser space
available to occupy between the pad and the substrate. This results
in it bulging outwards near the pinned contact line on the top, causing
repulsion.

@@

The findings can also be extended to other animals relying on oily
secretions for adhesion. Some ants, for example, show similar adhesion
on hydrophobic substrates under wet and dry conditions \cite{RN213},
similar to what we see in a ladybug. Recent experiments on
geckos revealed that they can attach well to fluoropolymer substrates
underwater while they show little adhesion to the same substrate in
air\cite{RN199,RN15}. Geckos are thought to rely on van der Waals
forces via dry contact with the substrate \cite{RN202}, although
recent observations of phospholipid footprints left behind walking
geckos \cite{RN205} could change that picture. Since geckos adhere
poorly to PTFE (surface energy $\sim$ 20 mN/m) one can
speculate that the phospholipid material has a higher surface energy,
and consequently makes a higher contact angle with PTFE in air. Let
us assume the phosopholipid substance to be a fluid similar to oil
with $\gamma_{fa}$= 30 mN/m and $\gamma_{fw}$= 42 mN/m such that
its contact angle with PTFE is 80\textdegree . Equation \ref{eq:theta_fw}
then gives us an underwater contact angle of 70\textdegree{} for the
phospholipid fluid. Thus, on a PTFE surface, the capillary bridge
model can predict a higher adhesion underwater than in air due to
its lower contact angle and higher interfacial energy underwater.
Based on similar assumptions, we predict the net adhesion force for
the gecko on different substrates (Figure \ref{fig:Comparison-with-model}).
The adhesion force predictions are in good qualitative agreement with
the whole animal experimental shear force values reported for the
gecko, with the trend of higher adhesion in air than underwater for
glass, similar adhesion in air and underwater for PMMA/OTS-SAM and
lower adhesion in air than underwater for PTFE. We, thus, propose
that the underwater experiments performed on geckos \cite{RN199,RN15}
indicate a capillary contribution to gecko adhesion. We suggest performing
single seta adhesion force tests similar to \citet{RN202}
using a hydrophilic and fluorinated probe in air and underwater conditions. 
If the fluorinated probe shows higher adhesion underwater than in air on a single seta, this
would confirm the role of capillary contributions due to an oil-like phospholipid layer to gecko adhesion.
